Generalization Errors of Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-09-08 arxiv/proof_main.tex
wip
revise

>>>>

Before the end of this section, we describe briefly the main ideas in the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.

\medskip
\noindent\textbf{An overview of the proofs of Lemmas \ref{lem_cov_shift} and \ref{lem_cov_derivative}.}
%We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
%We briefly describe the key ideas for proving Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
We use the standard Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}. Both Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} require a study of the matrix inverse $(X_1^\top X_1+X_2^\top X_2)^{-1}$ for $X_1= Z_1\Sigma_1^{1/2}$ and $X_2= Z_2\Sigma_2^{1/2}$. Suppose $M=\Sig_1^{1/2} \Sig_2^{-1/2}$ has a singular value decomposition
\be\label{eigen2}
M= U\Lambda V^\top, \quad \Lambda=\text{diag}( \lambda_1, \ldots, \lambda_p).
\ee
Then using equation \eqref{eigen2}, we can write
\be\label{eigen2extra}(X_1^\top X_1+X_2^\top X_2)^{-1}= \Sigma_2^{-1/2}V\left(   \Lambda U^\top Z_1^\top Z_1 U\Lambda  + V^\top Z_2^\top Z_2V\right)^{-1}V^\top\Sigma_2^{-1/2}.\ee
We divide the proof into the following parts.
\noindent\textbf{Defining the resolvents.} For our purpose, we introduce a convenient self-adjoint linearization trick, 
%This idea dates back at least to Girko, see e.g., the works \cite{girko1975random,girko1985spectral} and references therein. 
which has been proved to be useful in studying the local laws of random matrices of the Gram type \cite{Anisotropic, AEK_Gram, XYY_circular,DY20201}. We define the following $(p+n)\times (p+n)$ symmetric block matrix, which is a linear function of $Z_1$ and $Z_2$:
%\begin{definition}[Linearizing block matrix]\label{def_linearHG}%definiton of the Green function
%We define the $(n+N)\times (n+N)$ block matrix
 \begin{equation}\label{linearize_block}
    H(Z_1,Z_2): = n^{-1/2}\left( {\begin{array}{*{20}c}
   { 0 } & \Lambda U^{\top}Z_1^\top & V^\top Z_2^\top  \\
   {Z_1 U\Lambda  } & {0} & 0 \\
   {Z_2V} & 0 & 0
   \end{array}} \right).
 \end{equation}
For simplicity of notations, we define the index sets
$$\cal I_0:=\llbracket 1,p\rrbracket, \quad  \cal I_1:=\llbracket p+1,p+n_1\rrbracket, \quad \cal I_2:=\llbracket p+n_1+1,p+n_1+n_2\rrbracket ,\quad \cal I:=\cal I_0\cup \cal I_1\cup \cal I_2  .$$
 We will consistently use the latin letters $i,j\in\sI_{0}$, greek letters $\mu,\nu\in\sI_{1}\cup \sI_{2}$, and $\fa,\fb,\mathfrak c\in \cal I$. Correspondingly, the indices of the matrices $Z_1$ and $Z_2$ are labelled as 
 \be\label{labelZ}
 Z_1= (z_{\mu i}:i\in \mathcal I_0, \mu \in \mathcal I_1), \quad Z_2= (z_{\nu i}:i\in \mathcal I_0, \nu \in \mathcal I_2).\ee
Now we define the resolvents as follows. 
\begin{definition}[Resolvents]
We define the resolvent (or Green's function) of $H$ as
 \begin{equation}\label{eqn_defG}
 G (Z_1,Z_2,z):= \left[H(Z_1,Z_2)-\left( {\begin{array}{*{20}c}
   { z\id_{p}} & 0 & 0 \\
   0 & { \id_{n_1}}  & 0\\
      0 & 0  & { \id_{n_2}}\\
\end{array}} \right)\right]^{-1} , \quad z\in \mathbb C .
 \end{equation}
%It is easy to verify that the eigenvalues $\lambda_1(H)\ge \ldots \ge \lambda_{n+N}(H)$ of $H$ are related to the ones of $\mathcal Q_1$ through
%\begin{equation}\label{Heigen}
%\lambda_i(H)=-\lambda_{n+N-i+1}(H)=\sqrt{\lambda_i\left(\mathcal Q_2\right)}, \ \ 1\le i \le n\wedge N, \quad \text{and}\quad \lambda_i(H)=0, \ \ n\wedge N + 1 \le i \le n\vee N.
%\end{equation}
%and
%$$\lambda_i(H)=0, \ \ n\wedge N + 1 \le i \le n\vee N.$$
%where we used the notations $n\wedge N:=\min\{N,M\}$ and $n\vee N:=\max\{N,M\}$. 
%\begin{definition}[Index sets]\label{def_index}
and the resolvent of $  n^{-1}\left(\Lambda U^\top Z_1^\top Z_1 U\Lambda  + V^\top Z_2^\top Z_2V\right)$ as
\be\label{mainG}
\cal G(z):=\left( n^{-1}  \Lambda U^\top Z_1^\top Z_1 U\Lambda  + n^{-1}V^\top Z_2^\top Z_2V -z\right)^{-1},\quad z\in \C.
Moreover, we also define the following averaged resolvents, which are the (weighted) partial traces of $G$:
\be\label{defm}
\begin{split} 
m(z) :=\frac1p\sum_{i\in \cal I_0} G_{ii}(z) ,\quad & m_0(z):=\frac1p\sum_{i\in \cal I_0} \lambda_i^2 G_{ii}(z),\\
 m_1(z):= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}(z) ,\quad & m_2(z):= \frac{1}{n_2}\sum_{\nu\in \cal I_2}G_{\nu\nu}(z) .
\end{split}
\end{definition}
With Schur complement formula, we can check that
 \begin{equation} \label{green2}
 G (z):=  \left( {\begin{array}{*{20}c}
   { \cal G (z)} & \cal G(z)W  \\
   W^\top \cal G(z) & z (W^\top W - z)^{-1}
\end{array}} \right)^{-1}, %\quad \cal G_R:=(W^\top W - z)^{-1} ,
 \end{equation}
 where we abbreviated $W:=n^{-1/2}(\Lambda U^\top Z_1^\top, V^\top Z_2^\top)$. This shows that a control of $G(z)$ yields directly a control of $\mathcal G(z)$ as the upper-left block. On the other hand, $G(z)$ is a little  easier to use than $\cal G(z)$, and obviously contains more information. 
%one can find that %(recall equation \eqref{mainG})
%\be \label{green2}
%\begin{split}
%& \cal G_{L}=\left(WW^\top -z \right)^{-1} =\cal G ,\quad \cal G_{LR}=\cal G_{RL}^\top  = \cal G W , \quad \cal G_R= z\left(W^\top W - z\right)^{-1}.
%\end{split}
%, and the subindex of $\cal G_R$ means the lower-right block.

%Now using Schur complement formula, we can verify that the (recall equation \eqref{def_green})
%\begin{align} 
%G = \left( {\begin{array}{*{20}c}
%   { z\mathcal G_1} & \mathcal G_1 \Sig^{1/2} U^{*}X V\tilde \Sig^{1/2}  \\
%   {\tilde\Sig^{1/2}V^\topX^\top U\Sig^{1/2} \mathcal G_1} & { \mathcal G_2 }  \\
%\end{array}} \right) = \left( {\begin{array}{*{20}c}
%   { z\mathcal G_1} & \Sig^{1/2} U^{*}X V\tilde \Sig^{1/2} \mathcal G_2   \\
%   {\mathcal G_2}\tilde\Sig^{1/2}V^\topX^\top U\Sig^{1/2} & { \mathcal G_2 }  \\ 
%\end{array}} \right). \label{green2}
%\end{align}
%where $\mathcal G_{1,2}$ are defined in (\ref{def_green}).

\medskip
\noindent\textbf{Defining the asymptotic limits of the resolvents.} 
%\label{sec aymp_limit_G}
%\subsection{Resolvents and limiting law}
We now describe the asymptotic limit of $G(z)$ as $n\to \infty$. First we define the deterministic limits of $(m_1(z), m_{2}(z))$ by $\left(\frac{\rho_1+\rho_2}{\rho_1}a_{1}(z),\frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\right)$, where $(a_1(z), a_2(z))$ is
%\HZ{This $M_{1}, M_{2}$ notation is awkward; consider changing it to ${M}_1(z), {M}_2(z)$ (or  better, say $a_1(z), a_2(z)$? if they correspond to $a_1, a_2$ when $z=0$)}, 
the unique solution to the following system of equations
\begin{equation}\label{selfomega}
\begin{split}
& \frac{r_1}{a_{1}(z)} = \frac{1}{n}\sum_{i=1}^p \frac{\lambda_i^2}{  z+\lambda_i^2 a_{1}(z) +a_{2} (z) } - 1 ,\ \  \ \frac{r_2}{a_{2}(z)} = \frac{1}{n}\sum_{i=1}^p \frac{1 }{  z+\lambda_i^2 a_{1}(z) +  a_{2}(z)  }- 1 ,
\end{split}
\ee
satisfying that $\im a_{1}(z)>0$ and $\im a_{2}(z)>0$ for $z\in \C_+$ with $\im z$. 
%Here, for simplicity of notations, we introduced the following ratios 
%\be\label{ratios}
% \gamma_n :=\frac{p}{n}=\frac{1}{\rho_1+\rho_2},\quad r_1 :=\frac{n_1}{n}=\frac{\rho_1}{\rho_1+\rho_2},\quad r_2 :=\frac{n_2}{n}=\frac{\rho_2}{\rho_1+\rho_2}.
%\ee
We define the matrix limit of $G(z)$ as
\be \label{defn_piw}
\Pi(z) := \begin{pmatrix} -(z+a_{1}(z)\Lambda^2  +  a_{2}(z))^{-1} & 0 & 0 \\ 0 &  \frac{\rho_1+\rho_2}{\rho_1} a_{1}(z)\id_{n_1} & 0 \\ 0 & 0 & \frac{\rho_1+\rho_2}{\rho_2}a_{2}(z)\id_{n_2}  \end{pmatrix}.\ee
In particular, the matrix limit of $\cal G(z)$ is given by $-(z+a_{1}(z)\Lambda^2 + a_{2}(z))^{-1}$.

\medskip
\noindent{\bf Deriving the bias and variance asymptotics.} {\cor Notice that using equation \eqref{mainG}, we can write  equation \eqref{eigen2extra} as
\be\label{rewrite X as R} (X_1^\top X_1+X_2^\top X_2)^{-1}=n^{-1}\Sigma_2^{-1/2}V\cal G(0)V^\top\Sigma_2^{-1/2}.\ee
For the bias asymptotic limit, we show in \todo{where?} that
$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$

In the above definition, we have taken the argument of $\cal G$ to be a general complex number, because we will need to use $\cal G'(0)$ in the proof of Lemma \ref{lem_cov_derivative}, which requires a good estimate of $\cal G(z)$ for $z$ around the origin.

If $z=0$, then equation \eqref{selfomega} can be reduced to 
\begin{equation}\label{selfomega0}
\begin{split}
&a_1 + a_2= 1-\gamma_n,\quad    a_1 +\frac{\gamma_n}p\sum_{i=1}^p \frac{\lambda_i^2 a_1}{ \lambda_i^2 a_1+ (1-\gamma_n - a_1) }=r_1 .
\end{split}
\ee
where $a_1:=-r_1M_{1}(0)$ and $a_2:=-r_2M_{2}(0)$.

For the variance asymptotic limit, we study the resolvent
	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]

For the bias asymptotic limit, we show in \todo{where?} that
$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.
}

\medskip
\noindent{\bf Defining the resolvent minor.} \ 
%\HZ{Divide into several parts like sec 7 to improve readability.}
Then we define the resolvent minors, which are defined by removing certain rows and columns of the matrix $H$.

\begin{definition}[Resolvent minors]\label{defn_Minor}
 For any $ (p+n)\times (p+n)$ matrix $\cal A$ and $\fa \in \mathcal I$, we define the minor $\cal A^{(\mathfrak c)}:=(\cal A_{\fa\fb}:\fa,\fb \in \mathcal I\setminus \{\mathfrak a\})$ as the $ (p+n-1)\times (p+n-1)$ matrix obtained by removing the $\mathfrak c$-th row and column in $\cal A$. Note that we keep the names of indices when defining $\cal A^{(\mathfrak c)}$, i.e. $(\cal A^{(\mathfrak c)})_{\fa\fb}= \cal A_{\fa\fb}$ for $\fa,\fb \ne \mathfrak c$. Correspondingly, we define the resolvent minor as %(recall equation \eqref{green2})
\begin{align*}
G^{(\mathfrak c)}:&=\left[\left(H - \left( {\begin{array}{*{20}c}
   { zI_{p}} & 0  \\
   0 & { I_{n}}  \\
\end{array}} \right)\right)^{(\mathfrak c)}\right]^{-1} ,
%= \left( {\begin{array}{*{20}c}
%   { \mathcal G^{(\mathbb T)}} & \mathcal G^{(\mathbb T)} W^{(\mathbb T)}  \\
%   {\left(W^{(\mathbb T)}\right)^\top\mathcal G^{(\mathbb T)}} & { \mathcal G_R^{(\mathbb T)} }  \\
%\end{array}} \right)  ,
\end{align*}
and define the partial traces $m^{(\mathfrak c)}$ and $m^{(\mathfrak c)}_k$, $k=0,1,2,$ by replacing $G$ with $G^{(\mathfrak c)}$ in equation \eqref{defm}. For convenience, we will adopt the convention that for the resolvent minor $G^{(\mathfrak c)}$ defined as above, $G^{(\mathfrak c)}_{\fa\fb} = 0$ if $\fa =\mathfrak c$ or $\fb =\mathfrak c$.
\end{definition}

Note that the resolvent minor $G^{(\mathfrak c)}$ is defined such that it is independent of the entries in the $\mathfrak c$-th row and column of $H$. One will see a crucial use of this fact in the heuristic proof below.

\medskip
\noindent{\bf Schur complements and concentration.}
Now we give a heuristic derivation of the matrix limit when the entries of $Z_1$ and $Z_2$ are i.i.d. Gaussian. Note that in this case,
%However, notice that if the entries of $Z_1\equiv Z_1^{\text{Gauss}}$ and $Z_2\equiv Z_2^{\text{Gauss}}$ are i.i.d. Gaussian, then 
by the rotational invariance of the multivariate Gaussian distribution we have
\be\label{eq in Gauss} Z_1 U\Lambda \stackrel{d}{=} Z_1 \Lambda, \quad Z_2 V \stackrel{d}{=} Z_2,\ee
where ``$\stackrel{d}{=}$" means ``equal in distribution". Hence it suffices to consider the following resolvent  
 \begin{equation} \nonumber
   G(z)= \left( {\begin{array}{*{20}c}
   { -z\id_{p} } & n^{-1/2}\Lambda Z_1^\top & n^{-1/2} Z_2^\top  \\
   {n^{-1/2} Z_1 \Lambda  } & {-\id_{n_1}} & 0 \\
   {n^{-1/2} Z_2} & 0 & {-\id_{n_2}}
   \end{array}} \right)^{-1}.
 \end{equation}
Using Schur complement formula (see \alert{equation} (\ref{resolvent2}) \HZ{check other usage of equation ref}), we have that %for $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
\begin{align}
\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu,\nu\in \mathcal I_1} z_{\mu i}z_{\nu i}G^{\left( i \right)}_{\mu\nu} - \frac{1}{n} \sum_{\mu,\nu\in \mathcal I_2} z_{\mu i}z_{\nu i}G^{\left( i \right)}_{\mu\nu} -2 \frac{\lambda_i}{n} \sum_{\mu\in \cal I_1,\nu\in \mathcal I_2} z_{\mu i}z_{\nu i}G^{\left( i \right)}_{\mu\nu},  \ \ \text{for }\  i \in \cal I_0 , \label{0self_Gii}\\
\frac{1}{{G_{\mu\mu} }}&=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}\lambda_i \lambda_j z_{\mu i}z_{\mu j} G^{\left(\mu\right)}_{ij}, \quad \frac{1}{{G_{\nu\nu} }}=  - 1 - \frac{1}{n} \sum_{i,j\in \mathcal I_0}  z_{\nu i}z_{\nu j}  G^{\left(\nu\right)}_{ij},  \ \ \text{for }\  \mu \in \cal I_1, \ \nu\in \cal I_2, \label{0self_Gmu1} 
\end{align}
where we recall the notations in equation \eqref{labelZ}. For the right-hand side of equation \eqref{0self_Gii}, $G^{(i)}$ is independent of the entries $z_{\mu i}$ and $z_{\nu i}$. Hence by the concentration inequalities in Lemma \ref{largedeviation}, we have that the  right-hand side of equation \eqref{0self_Gii} concentrates around the partial expectation over the entries $\{z_{\mu i}: \mu \in \cal I_1\cup \cal I_2\}$, i.e., with high probability,
\begin{align*}
\frac{1}{{G_{ii} }}&=  - z - \frac{\lambda_i^2}{n} \sum_{\mu \in \mathcal I_1}  G^{\left( i \right)}_{\mu\mu} - \frac{1}{n} \sum_{\mu\in \mathcal I_2} G^{\left( i \right)}_{\mu\mu} +\oo(1)= - z - \lambda_i^2 r_1 m_1^{(i)}(z)-  r_2m_2^{(i)}(z)+\oo(1),  
\end{align*}
where we used the definition of $m_1^{(i)}$ and $m_2^{(i)}$ in equation \eqref{defm} with $G$ replaced by $G^{(i)}$. Intuitively, since we have only removed only one column and one row out of the $(p+n)$ columns and rows in $H$, $m_1^{(i)}$ and $m_2^{(i)}$ should be close to the original $m_1$ and $m_2$. Hence we obtain from the above equation that
\begin{align}\label{1self_Gii}
 G_{ii}  = -\frac{1}{ z +\lambda_i^2 r_1  m_1(z) + r_2 m_2(z)+\oo(1)}.
\end{align}
Similarly, we can obtain from equation \eqref{0self_Gmu1} that for $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
\be\label{1self_Gmu} G_{\mu \mu }=-\frac{1}{1+\gamma_n m_0 + \oo(1)},\quad G_{\nu\nu}=-\frac1{1+\gamma_n m+\oo(1)},\ee
with high probability.

\medskip
\noindent\textbf{Deriving the self-consistent equations.} Taking average we obtain that 
\be\label{2self_Gmu} m_1= \frac{1}{n_1}\sum_{\mu \in \cal I_1}G_{\mu\mu}=-\frac{1}{1+\gamma_n m_0 + \oo(1)},\quad m_2=\frac{1}{n_2}\sum_{\nu \in \cal I_2}G_{\nu\nu}=-\frac{1}{1+\gamma_n m + \oo(1)},
\ee
with high probability. Together with the definition of $m$ and $m_0$ in equation \eqref{defm}, the two equations in equation \eqref{2self_Gmu} give that 
\be\label{3self_Gmu}  \frac1{m_1}= -1- \frac{\gamma_n}{p} \sum_{i=1}^p \lambda_i^2 G_{ii}+ \oo(1),\quad \frac1{m_2}=-1-\frac{\gamma_n}{p} \sum_{i=1}^p G_{ii}  + \oo(1),\ee
with high probability. Plugging equation \eqref{1self_Gii} into equation \eqref{3self_Gmu}, we obtain that
\begin{align*}
& \frac1{m_1}= -1+ \frac{\gamma_n}{p} \sum_{i=1}^p \frac{\lambda_i^2 }{ z +\lambda_i^2 r_1  m_1(z) + r_2 m_2(z)+\oo(1)}+ \oo(1),\\ 
& \frac1{m_2}=-1+\frac{\gamma_n}{p} \sum_{i=1}^p \frac{1}{ z +\lambda_i^2 r_1  m_1(z) + r_2 m_2(z)+\oo(1)}  + \oo(1),
\end{align*}
with high probability, which give the approximate self-consistent equations for $(m_1,m_2)$. Compare them to the deterministic self-consistent equations in equation \eqref{selfomega}, one can observe that we should have $(m_1,m_2) =(M_{1}, M_{2})+\oo(1)$ with high probability.

\medskip
\noindent\textbf{Deriving the matrix limit.} Inserting this approximate identity into equation \eqref{1self_Gii}-equation \eqref{2self_Gmu}, we see that for  $i \in \cal I_0$, $\mu \in \cal I_1$ and $\nu\in \cal I_2$,
$$G_{ii}=-(z +\lambda_i^2 r_1  M_{1} + r_2 M_{2}+\oo(1))^{1/2},\quad G_{\mu\mu}=M_{1}+\oo(1),\quad G_{\nu\nu}=M_{2}+\oo(1),$$
with high probability. These explain the diagonal entries of $\Pi$ in equation \eqref{defn_piw}. For the off-diagonal entries, they are close to zero due to concentration. For example, for $i\ne j\in \cal I_1$, by Schur complement formula (see (\ref{resolvent3})), we have
$$G_{ij}=-G_{ii}\left(\frac{\lambda_i}{n^{1/2}}\sum_{\mu \in \cal I_1} z_{\mu i} G^{(i)}_{\mu j} + \frac{1}{n^{1/2}}\sum_{\mu \in \cal I_2} z_{\mu i} G^{(i)}_{\mu j} \right).$$
Using Lemma \ref{largedeviation}, we can show that $n^{-1/2}\sum_{\mu \in \cal I_1} z_{\mu i} G^{(i)}_{\mu j}$ and $n^{-1/2}\sum_{\mu \in \cal I_2} z_{\mu i} G^{(i)}_{\mu j}$ are both close to zero. The other off-diagonal entries can be bounded in the same way.

The above arguments are the core of the main proof. To have a rigorous proof, we need to estimate each error carefully, and extend the Gaussian case to the more general case where the entries of $Z_1$ and $Z_2$ only satisfy certain moment assumptions. These will make the real argument rather tedious, but the methods we used are standard in the random matrix literature \cite{erdos2017dynamical,Anisotropic}. For the full proof, we refer the reader to ... .

### 2020-09-08 arxiv/transfer.tex
revise

\medskip
\noindent\textbf{Proof overview.}
%We first describe the proof of Theorem \ref{lem_cov_shift_informal}.
We briefly describe the key ideas for proving Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.
We use the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}.

For the variance asymptotic limit, we study the resolvent
	\[ R(z):= \bigbrace{\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2} - z \id}^{-1}, \text{ for any } z\in \C \text{ around } z=0. \]
Using the techniques from \citet{Anisotropic} and \citet{yang2019spiked}, we find the asymptotic limit of $R(z)$ for any $z$ as $p$ goes to infinity, denoted by $R_\infty(z)$, with an almost optimal convergence rate of $p$.
In particular, when $z=0$, the asymptotic limit of equation \eqref{lem_cov_shift_eq} is given by
	\[ \tr[\Sigma_2^{-1/2} \Sigma \Sigma_2^{-1/2}R_\infty(0)]. \]

For the bias asymptotic limit, we show in \todo{where?} that
$$\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} w}^2= w^\top \Sigma_2^{-1/2}R'(0)\Sigma_2^{-1/2} w.$$
Hence its limit can be calculated through $R_\infty'(z)$, which gives the expression in \eqref{lem_cov_derv_eq}.
We leave the full proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative} to Appendix \ref{sec_maintools}.
Combining the above two results, we provide the proof of Theorem \ref{thm_main_informal} in Section \ref{app_proof_main_thm}.

>>>>

In Section \ref{app_proof_main_thm}, we will describe briefly the main ideas in the proof of Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}. In particular, we will give a simple (although not totally rigorous) derivation of the equations \eqref{eq_a12extra} and \eqref{eq_a34extra}.
